Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-01 paper/paper.tex
updated kafka section

  \centering
    \includegraphics[width=\textwidth, height=.4\textheight]{flink_engine.png}
     \caption{ An example of data flow graph \cite{flink}.}
\end{figure} 
\subsection{Apache Kafka}
\par Apache Kafka is scalable, fault-tolerant distributed publish/subscribe streaming framework \cite{kafka}.
It manges the stream records in different categorizes (i.e., topics) that portioned and distributed over the servers in the Kafka cluster. It allows the data producers to publish stream of records to certain Kafka topic. While the consumer applications can subscribe to one or more topic to read the data stream. It has been widely  adopted, for example, 
Spark and Flink can receive data stream from Kafka.

@@

\bibitem[8]{kafka} 
Apache Kafka. Available: https://kafka.apache.org/ [Accessed February 2017].

>>>>

  \centering
    \includegraphics[width=\textwidth, height=.4\textheight]{flink_engine.png}
     \caption{ An example of data flow graph \cite{flink}.}
\end{figure} 
\subsection{Apache Kafka}
\par Apache Kafka is scalable, fault-tolerant distributed publish/subscribe streaming framework \cite{kafka}.
It manges the stream records in different categorizes (i.e., topics) that portioned and distributed over the servers of the Kafka cluster. It allows the data producers to publish stream of records to certain Kafka topic. While the consumer applications can subscribe to one or more topic to read the data stream. The consumers are grouped into groups based on the group name that allows Kafka to distribute and balance the stream partitions among the  members of a certain group for the sake of scalability. Figure 3 shows how 4 partitions of stream is distributed differentially between two groups of consumers based on the number of members. 
Apache Kafka has been widely  adopted, for example, 
Spark and Flink can receive data stream from Kafka.

  \centering
    \includegraphics[width=\textwidth, height=.3\textheight]{kafka_groups.png}
     \caption{ Distribution of stream partitions for consumer groups in Kafka \cite{kafka}.}
\end{figure}

@@

\bibitem[8]{kafka} 
Apache Kafka. Available: https://kafka.apache.org/intro.html [Accessed February 2017].
